---
title: "R Notebook"
output: html_notebook
---
# Init.
```{r setup} 
library(wholebrain)

```
# Get images
Get the image(s) you want to process.
```{r}
mouse="m1060"
sectionNumber = "2"
subfolder = paste(mouse,sectionNumber,sep = "-", collapse=NULL)
folder<-file.path(getwd(), "..", mouse,subfolder)
imagefile<-list.files(folder, full.names=TRUE)
```

# Segment out neurons and the brain outline from autofluorescence.
```{r}
seg<-wholebrain::segment(imagefile)
```
# Quickly Plot the images
```{r}
plot(seg$soma$x, seg$soma$y,ylim=rev(range(seg$soma$y,asp=1)))
```

#Registration
```{r}
quartz()
regi<-registration(imagefile, coordinate= 0.14, filter=seg$filter)
```
```{r}
regi<-add.corrpoints(regi, 3)
```
Plot Corrected Points
```{r}
regi<-registration(imagefile, coordinate= -2.06, filter=seg$filter, correspondance = regi)
```

# Save out the registration
```{r}
save(seg, regi, file='m1060.Rdata')
```

# Plot Cells on Atlas
```{r}
dataset<-inspect.registration(regi, seg, forward.warps = TRUE)
```

# Save Plots
```{r}
mainDir <- file.path(getwd(), mouse,subfolder)
subDir <- "plots"
if (file.exists(file.path(mainDir,subDir))){
} else {
    dir.create(file.path(mainDir, subDir))
}
filename = paste(file.path(getwd(),"plots") , "inspectRegi.pdf",sep = "_", collapse=NULL)
quartz.save(file.path(saveFolder,filename),type="pdf")
```

dot.plot(dataset)
filename = paste(list.files(saveFolder) , "plot.pdf",sep = "_", collapse=NULL)
quartz.save(file.path(saveFolder,filename),type="pdf")

